Group assignment

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

>>>>

### Correlation - what we can expect we opting for higher price?
#### We may see that higher price is linked to proximity to the city center, higher rating, and more reviews.
```{r echo=FALSE}
# subset
df3<-df2[c("price","trueprice","actualrating","rating_reviewcount","distance")]
correlationt<-funModeling::correlation_table(data=df3, target="price") 
```
```{r echo=FALSE}
kable(correlationt)
```
